Black swans in ecological time series\\ Black swans in population dynamics\\ Heavy-tailed ecological time series\\ Black swans in ecological dynamics\\ Black swan ecological dynamics\\ \ldots

### 2014-11-06 text/supp.tex
Add alternative prior plot to SOM

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=\textwidth]{../analysis/sim-gompertz.pdf}
\caption{
TODO WILL REMOVE ALL OR MOST OF THIS
  Simulation testing the Gompertz estimation model when the process deviation
  draws were chosen so that $\nu$ could be estimated close to the true value
  outside the full population model (``effective $\nu$'' within a CV of 0.2 of
  specified $\nu$). The simulation was run across population $\nu$ values
  (columns) and different scenarios (colours): (1) 100 time steps and no
  observation error, (2) 50 time steps and no observation error, (3) 50 time
  steps and observation error drawn from $\mathrm{Normal} (0, 0.2^2)$ but
  ignored, and (4) 50 time steps with observation error in which the quantity
  of observation error was assumed known. Dashed horizontal lines show the true
  population values; these true values were chosen to represent approximately
  the median values as estimated from the Global Population Dynamics Database.
  Individual dots and lines
  represent a stochastic draws from the true population distribution and
  a model fitting (median and 80\% credible intervals). The panels from top to
  bottom show $1/\nu$, process noise scale parameter $\sigma$, growth rate
  parameter $\lambda$, and the density dependence parameter $b$.
}
\label{fig:sim-gompertz}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=\textwidth]{../analysis/sim-gompertz-boxplots.pdf}
\caption{
TODO WILL REMOVE ALL OR MOST OF THIS
  The distribution of median estimates from the same simulation as described in
  Fig.~\ref{fig:sim-gompertz}. The boxes show the interquartile range. The
  whiskers extend to $1.5$ times the interquartile range and outliers are shown
  as dots. Note that these distributions represent the output from only 20
  simulation iterations, so there is some level of remaining sampling noise.
}
\label{fig:sim-gompertz-boxplots}
\end{center}
\end{figure}

>>>>

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=\textwidth]{../analysis/gomp-prior-comparison.pdf}
\caption{
Estimates of $\nu$ from Gompertz models with alternative priors on $\nu$. Shown are medians of the posterior (dots) and 50\% credible intervals (segments). The diagonal line indicates a one-to-one relationship. Different colours indicate various taxonomic classes. The grey-shaded regions indicate regions of disagreement if $\nu = 10$ is taken as a threshold of heavy-tailed dynamics. The base, weaker, and stronger priors on $\nu$ are illustrated in Fig.~\ref{fig:priors}. In general, the estimates are nearly identical in cases where the data are informative about low values of $\nu$. When the data are less informative about low values of $\nu$, the prior can slightly pull the estimates of $\nu$ towards higher or lower values.
}
\label{fig:alt}
\end{center}
\end{figure}

@@

% \begin{figure}[htbp]
% \begin{center}
% \includegraphics[width=\textwidth]{../analysis/sim-gompertz.pdf}
% \caption{
% TODO WILL REMOVE ALL OR MOST OF THIS
%   Simulation testing the Gompertz estimation model when the process deviation
%   draws were chosen so that $\nu$ could be estimated close to the true value
%   outside the full population model (``effective $\nu$'' within a CV of 0.2 of
%   specified $\nu$). The simulation was run across population $\nu$ values
%   (columns) and different scenarios (colours): (1) 100 time steps and no
%   observation error, (2) 50 time steps and no observation error, (3) 50 time
%   steps and observation error drawn from $\mathrm{Normal} (0, 0.2^2)$ but
%   ignored, and (4) 50 time steps with observation error in which the quantity
%   of observation error was assumed known. Dashed horizontal lines show the true
%   population values; these true values were chosen to represent approximately
%   the median values as estimated from the Global Population Dynamics Database.
%   Individual dots and lines
%   represent a stochastic draws from the true population distribution and
%   a model fitting (median and 80\% credible intervals). The panels from top to
%   bottom show $1/\nu$, process noise scale parameter $\sigma$, growth rate
%   parameter $\lambda$, and the density dependence parameter $b$.
% }
% \label{fig:sim-gompertz}
% \end{center}
% \end{figure}

@@

% \begin{figure}[htbp]
% \begin{center}
% \includegraphics[width=\textwidth]{../analysis/sim-gompertz-boxplots.pdf}
% \caption{
% TODO WILL REMOVE ALL OR MOST OF THIS
%   The distribution of median estimates from the same simulation as described in
%   Fig.~\ref{fig:sim-gompertz}. The boxes show the interquartile range. The
%   whiskers extend to $1.5$ times the interquartile range and outliers are shown
%   as dots. Note that these distributions represent the output from only 20
%   simulation iterations, so there is some level of remaining sampling noise.
% }
% \label{fig:sim-gompertz-boxplots}
% \end{center}
% \end{figure}
